---
title: "Web Scraping Hong Kong Property Price"
author: "Fung YIP"
date: "14 August 2016"
output: html_document
---

## 美聯物業樓價

This handy R script is created to extract Hong Kong **Gross** and **Net** property prices from the Hong Kong Estate Agent Midland 美聯物業 <http://www.midland.com.hk/> for rapid machine learning.

### Data Collection
Hong Kong Property Price Movement is sourced from Midland Realty
```{r url}
url <- "http://resources.midland.com.hk/json/common/price.json?t="
```

```{r library}
library(readr)
library(tidyverse)
library(lubridate)
library(timekit)
library(ggplot2)
library(forecast)
library(sweep)
library(zoo)
```

### Web Scraping
```{r WebScraping, echo=TRUE, message=FALSE, warning=FALSE}
require(jsonlite)
flat_data<-fromJSON(url)
period<-flat_data$x_axis$labels$labels
Price<-flat_data$elements
```

###Data manipulation
```{r prices, echo=TRUE, message=FALSE, warning=FALSE}
net_price<-as.data.frame(Price$values[[1]])
gross_price<-as.data.frame(Price$values[[2]])
```

```{r}
data <- net_price %>% 
  mutate(net_price = Price$values[[1]]) %>% 
  mutate(gross_price = Price$values[[2]]) %>% 
  mutate(date = seq(ymd('1997-01-01'),ymd('2017-11-01'), by = 'month')) %>% 
  select(date, net_price, gross_price)
```

```{r Chart}
data %>%
    ggplot(aes(date, net_price)) +
    geom_line() +
    scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
    labs(title = "Hong Kong Property Price: 1997 through 2017")
```


```{r dataout}
write_csv(data, "../DataOut/hk_property_price.csv")
```

Add Time dimension and select net price 
```{r Add Time Dimension}
data_ts <- data %>%
  select(date, net_price) %>% 
  tk_ts(start = c(1997,1), frequency = 12)
```

```{r ARIMA}
# Model using auto.arima
fit_arima <- data_ts %>% 
  auto.arima
fit_arima
```

#sw_tidy():Used to retrieve the model coefficients
```{r}
sw_glance(fit_arima) %>% 
  glimpse()
```

#sw_glance(): Used to retrieve model description and training set accuracy metrics

```{r}
# sw_augment - get model residuals
sw_augment(fit_arima, timetk_idx = TRUE)

```


```{r}
# Plotting residuals
sw_augment(fit_arima, timetk_idx = TRUE) %>%
    ggplot(aes(x = index, y = .resid)) +
    geom_point() + 
    geom_hline(yintercept = 0, color = "red") + 
    labs(title = "Residual diagnostic") +
    scale_x_date(date_breaks = "2 year", date_labels = "%Y") 
```


```{r}
# Forecast next 12 months
fcast_arima <- forecast(fit_arima, h = 12)
class(fcast_arima)
```

```{r}
# sw_sweep - tidies forecast output
fcast_tbl <- sw_sweep(fcast_arima, timetk_idx = FALSE)
fcast_tbl
```


```{r}
# Visualize the forecast with ggplot
fcast_tbl %>%
    ggplot(aes(x = index, y = net_price, color = key)) +
    # 95% CI
    geom_ribbon(aes(ymin = lo.95, ymax = hi.95), 
                fill = "#D5DBFF", color = NA, size = 0) +
    # 80% CI
    geom_ribbon(aes(ymin = lo.80, ymax = hi.80, fill = key), 
                fill = "#596DD5", color = NA, size = 0, alpha = 0.8)+
  geom_line()+
  labs(title = "Hong Kong Property Price: 1997 through 2017")

```























Export
```{r DataOut, echo=TRUE, message=FALSE, warning=FALSE}
ggsave(filename="../DataOut/hk_flat_net_price.png",plot=hk_flat_net_price)
```

